Java Based Memory Latency Simulator

### 2020-11-16 finalPaper/paper.tex
Fixed some formatting errors. Also completed Sec. 2

In Section~\ref{sec:memlate} we discuss abstractly how the memory latency 
simulator works. Section ~\ref{sec:build} we describe how to build and run the 
simulator. In section ~\ref{sec:expstats} we explain all the types of 
information collected from the simulator. Then, in ~\ref{sec:data} we 
present the actual data collected from the simulator, as well as actual 
real world data. Section ~\ref{sec:disc} goes on to explain any discrepencies 
found between our data and the real world collected data. Finally, in
~\ref{sec:conclusions} we summarize our results, as well as report what
we have learned, and suggest how this simulator could be better
improved or used.

@@

Insert detailed description of the code here. 
Also describe components and terms as you go.

>>>>

In Section~\ref{sec:memlate} we discuss abstractly how the memory latency 
simulator works, and why we built it. Section~\ref{sec:build} describes
how to build and run the simulator. In section~\ref{sec:expstats} we explain
all the types of  information collected from the simulator. Then, in section~\ref{sec:data}
we present the actual data collected from the simulator, as well as actual 
real world data. Section~\ref{sec:disc} goes on to explain any discrepencies 
found between our data and the real world collected data. Finally, in~\ref{sec:conclusions}
we summarize our results, as well as report what
we have learned, and suggest how this simulator could be better
improved or used.

@@

\subsection{Abstract Definition}
The goal of this project was to create a Java based simulator that will allow
semi-low access to artificial data so the user could gather statistics and trends
from moving this data around the artificial system. The simulator consists of four
primary parts: memSim, which is essentially the contoller; a CPU with one level of cache;
one or more sticks or RAM; and one or more hard drive disks.

Each component's (CPU, RAM, HDD), storage is represented with a byte array.
The user then has options to handle data on any component via the memSim terminal interface.

\subsection{Primary Audience}
Today, there are many levels of abstraction between the high-level user and their hardware.
We wanted to give a way to collect data at this low level of hardware, but not have
to be a electrical engineer working on the circuitry.

In our research, there is also very little public access on this type of data, so
it could be useful for researchers and students alike to use this simulator to collect
data for a variety of projects.
